---
title: "Ice time lapse analysis"
output: html_document
---

## Updates and _TODO_ list
1. Scrape EXIF data, get timecoded
1. Plot stacked
1. Vizualization across a ransect
1. Other metrics,
    1. Split the field into eights, and look at % in each?
    2. # of cells?

## Getting started.

Let's load up a bunch of photos

```{r}
library(EBImage)
pics<-dir(pattern=".JPG")  ## Load a directory of images
head(pics)
p1<-readImage(pics[5]) ## Read a picture 
fp<-flip(p1) ### Rotate
```

And let's plot it (`r paste(p1)`):

```{r}
display(fp, method="raster")  ## Display again
```

We can convert it to grayscale (useful for analysis)
```{r}
colorMode(fp) = Grayscale ## switch to grayscale
display(fp, method="raster") ## chec via display
```

And then we want to crop it for just the ice
```{r}
ffp<-getFrame(fp,1, type='total') ### isolate frame #1
goof<-ffp[1:2560, 830:1300] ### crop to just the ice
display(goof, method="raster") ### display it
```

And now we can ask questions like what is the distribution of brightness across pixels

```{r}
library(ggplot2)
bv<-c(as.numeric(goof))
hist(as.numeric(goof))
```

But EBImage is fancy, and maybe we want to do some pre-processing of the image, here
```{r}
flo = makeBrush(21, shape='disc', step=FALSE)^2
flo = flo/sum(flo)
iceflo = filter2(goof, flo)
fhi =  matrix(1, nc=3, nr=3)
fhi[2,2] = -8
icefhi = filter2(goof, fhi)
display(iceflo, method="raster") ### Low pass filter
display(icefhi, method="raster") ### High pass filter
```
Or we can just do a contrast adjustment
ORIGINAL
```{r}
display(goof, method="raster")
```
Contrast (*2)
```{r}
display(goof*2, method="raster")
```

__TODO__ a panel that shows ice, and a histogram of brightness values simultaneously for review.  _TODO_ Do some multiple plotting in base r with histo and raster display

## Contact
Abe Borker (aborker@ucsc.edu)